---
title: "Generate actigraphy summary"
author: "Cory Holdom"
format:
  html: default
  gfm: default
editor: visual
echo: true
---

```{r Document information}
#| output: false
## ---------------------------
##
## Script name: 
##
## Purpose of script:
##
## Author: Dr. Cory Holdom
##
## Date Created: 2025-06-11
##
## Copyright (c) Cory Holdom, 2025
## Email: cory.holdom@ndcn.ox.ac.uk
##
## ---------------------------
##
## Notes:
##   
##
## ---------------------------

memory.limit(30000000)     # this is needed on some PCs to increase memory allowance, but has no impact on macs.

## ---------------------------

## load up the packages we will need:  (uncomment as required)

# require(tidyverse)
# require(data.table)
# source("functions/packages.R")       # loads up all the packages we need

## ---------------------------

## load up our functions into memory

# source("functions/summarise_data.R") 

## ---------------------------
```

## Overview

Details of activity metrics reported for activity summary metrics.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
